### 2012-10-02 docs/visualization/visualization.tex
remove lens stuff -- it is in managing jobs now
add plot_pidivu

@@

%-----------------------------------------------------------------------------
% data_procesing
%-----------------------------------------------------------------------------
\section{Visualizing with {\tt data\_processing} scripts}
\label{sec:vis:python}

{\tt data\_processing/python\_plotfile} provide a simple commandline
tool for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

>>>>

{\tt pi\_divu}         & $\pi \nabla \cdot \tilde{\Ub}$ (a measure of energy conservation) & {\tt plot\_pidivu} \\

@@

%-----------------------------------------------------------------------------
% data_procesing
%-----------------------------------------------------------------------------
\section{Python visualization scripts}
\label{sec:vis:python}

{\tt AmrPostprocessing/F\_Src/python\_plotfile} provide a simple commandline
tool for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.
